\documentclass[a4paper]{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{scrextend}
\usepackage{graphicx,calc}
\usepackage{fontawesome}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[
    bookmarks, colorlinks, breaklinks, unicode,
    pdftitle={Melissa Ross - Resume},
    pdfauthor={Melissa Ross},
    pdfproducer={}
]{hyperref}

\textheight=10in
\pagestyle{empty}
\raggedright
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=MidnightBlue}
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }
\pagestyle{plain}

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
    \vspace{2mm}
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%



\begin{document}
\vspace*{-50pt}

    

%==== Profile ====%

\begin{minipage}[t]{0.5\textwidth}
    \vspace{-24pt}
    {\Huge\scshape{Melissa Ross}}\\
    Boston, MA
\end{minipage}
\begin{minipage}[t]{0.48\textwidth}
    \flushright 
    \begin{tabular}[h]{ll@{}}
        \faEnvelope & \href{mailto:amazastic@gmail.com}{amazastic@gmail.com}\\
        \faPhone    & 315-521-0638\\
        \faLinkedin & \href{http://www.linkedin.com/in/melissa-elizabeth-ross/}{linkedin.com/in/melissa-elizabeth-ross}
    \end{tabular}
\end{minipage}


\vspace{8mm}

\setlength{\parindent}{4ex}
Creative, friendly, detail oriented, and well organized team player with experience in event 
planning, teaching, hospitality, and administrative operations. Actively involved in the Boston 
startup community. Naturally warm and welcoming with a strong artistic and design side.

\setlength{\parindent}{0ex}
\vspace{4mm}

%==== Technical Skills ====%
\header{\faGear \hspace{1pt} Technical Skills}
\begin{tabular}[h]{@{}ll}
Office Software: &       Google Docs/Sheets/Slides, Powerpoint, Word, Excel \\[4pt]
Design Tools: &          Photoshop, Illustrator \\[4pt]
Language: &             Conversational Spanish
\end{tabular}

\vspace{4mm}

%==== Experience ====%
\header{\faBriefcase \hspace{1pt} Experience}
\vspace{1mm}

\textbf{\textsc{Linnaean Community School}} \hfill Cambridge, MA\\
\vspace{2mm}

\begin{addmargin}[1em]{0em}
    \textit{Teacher} \hfill August 2014 - Present\\
    \vspace{-1mm}
    \begin{itemize} \itemsep 1pt
        \item Designed and taught after school classes for elementary, middle, and high 
            school students. Classes ranged from comic book design, reading comprehension,
            to illustration.
        \item Ran study hall, a program to help children who have fallen behind in their
            school work. Actively worked with the children on their homework in whatever
            subject they were behind in.
        \item Co-led the after school activities club, overseeing over 40 children and leading
            them through different interactive activities.
        \item Performed tuition bookkeeping and followed up with parents on
            missing payments.
        \item In charge of keeping parents informed of administrative updates, events,
            and workshops through regular notices and letters.
        \item Planned and organized after school field trips. Booked venues, acquired 
            necessary permits and wavers, organized transportation, and chaperoned the
            children during the trip.
        
        
    \end{itemize}
    \textit{Inclusion Specialist} \hfill August 2015 - May 2017\\
    \vspace{-1mm}
    \begin{itemize} \itemsep 1pt
        \item Worked one-on-one with children with special needs, trauma, and behavioral
            issues, who are on individual education plans (IEP). Made sure children stayed
            focused, on-task, and integrated into the classroom experience.
        \item Provided parents daily updates and feedback on their child's behavior and
            progress.

    \end{itemize}
\end{addmargin}

\textbf{\textsc{Camp Seafaring}} \hfill Cambridge, MA\\
\vspace{2mm}

\begin{addmargin}[1em]{0em}

\textit{Counselor} \hfill Summers 2014 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Organized and led art activities and games.
    \item Organized, booked, and chaperoned camp field trips and outings.
    \item Performed camp and school tuition bookkeeping.
\end{itemize}
\end{addmargin}


\textbf{\textsc{Independent Event Planner}} \hfill Cambridge, MA\\
\vspace{2mm}
\begin{addmargin}[1em]{0em}
\textit{} \hfill June 2011 - June 2014\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Booked local artists, musicians, and comedians for venues.
    \item Negotiated business arrangements between venues and artists.
    \item Designed event experience.
    \item Responsible for event marketing through social media and flyers.
    \item Managed event set-up, MC'ed during event, and managed tear-down.
\end{itemize}
\end{addmargin}

\textbf{\textsc{Rosie’s Bakery}} \hfill Cambridge, MA\\
\vspace{2mm}
\begin{addmargin}[1em]{0em}
\textit{Supervisor} \hfill June 2011 - June 2014\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Oversaw staff and enforced policies and procedures for food safety, 
        point of sale, and hospitality.
    \item Managed deliveries, inventory, and ordering.
    \item Performed cashier balancing at the end of every day and sent the resulting
        report to corporate.  
    \item Responsible for resolving customer complaints.
    \item Trained new staff.
\end{itemize}
\end{addmargin}

\textbf{\textsc{Democratic National Committee}} \hfill Boston, MA\\
\vspace{2mm}

\begin{addmargin}[1em]{0em}

\textit{Neighborhood Outreach Field Manager} \hfill May 2008 - October 2008\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Led door-to-door canvasing missions and developed canvasing strategy based on
        the team and neighborhood.
    \item Trained new outreach staff.
    \item Ran office workshops on how to keep engagement with possible
        donors.
    \item Maintained and kept track of canvasing data including engagement and donation
        numbers per neighborhood.
\end{itemize}

\end{addmargin}

%==== Lab =====%
\textbf{\textsc{Finger Lakes Arts Grants and Services}} \hfill Geneva, NY\\
\vspace{2mm}

\begin{addmargin}[1em]{0em}

\textit{Intern} \hfill 2006 - 2007\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Wrote articles for “Expressions” E-Newsletter, a publication meant to keep the
        Finger Lakes community connected to local artists and art-related events.
    \item Researched various art-related topics and interviewed local artists for 
        newsletter articles.
    \item Researched local artists and collated reports to grant-giving institutions for
        their consideration.
    \item Maintained website's art events calendar. 
\end{itemize}
\end{addmargin}


\header{\faHeart \hspace{1pt} Volunteering}

\textbf{\textsc{Artisans Asylum}} \hfill Somerville, MA\\
\begin{addmargin}[1em]{0em}
\vspace{2mm}
\textit{Volunteer} \hfill April 2018 - August 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Worked the desk, greeting and singing in visitors. Answered phone,
    greeted visitors, gave tours, registered new members, signed in students, 
    handled mail and packages, and answered emails.
\end{itemize}
\end{addmargin}

\textbf{\textsc{San Miguel Orphanage}} \hfill Lima, Peru\\
\begin{addmargin}[1em]{0em}
\vspace{2mm}
\textit{Volunteer} \hfill June of 2007\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Helped children with homework.  Organized and led creative group activities.
        Assisted young adults with special needs. Organized local fund and used fund money
        to buy needed blankets, shoes and other essentials.
\end{itemize}
\end{addmargin}

\textbf{\textsc{Newton Wellesley Hospital ER}} \hfill Newton, MA\\
\begin{addmargin}[1em]{0em}
\vspace{2mm}
\textit{Volunteer} \hfill Fall of 2007\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Prepared rooms for patients with necessary supplies. Oversaw waiting room and
        guided new arrivals. Reassured and comforted patients. When needed, interpreting 
        patient’s requests from Spanish to English.
\end{itemize}
\end{addmargin}

\textbf{\textsc{Escuela Popular de Arte}} \hfill Santiago de los Caballeros, Dominican Republic\\
\begin{addmargin}[1em]{0em}
\vspace{2mm}
\textit{Volunteer} \hfill March 2006 - August 2006\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Instructed and supervised students in art classes. Coordinated and directed student 
        performance for local community. 
\end{itemize}
\end{addmargin}

\textbf{\textsc{MSPCA}} \hfill Boston, MA\\
\begin{addmargin}[1em]{0em}
\vspace{2mm}
\textit{Volunteer} \hfill March 2006 - August 2006\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Worked as admin in the referral office. Updated out-of-date profile information 
        for donations.
\end{itemize}
\end{addmargin}
\vspace*{4mm}


%==== Education ====%
\header{\faGraduationCap \hspace{1pt} Education}
\textbf{Hobart and William Smith}\hfill Geneva, NY\\
Bachelors of Arts \\
Majors: Spanish and Hispanic Studies, Media and Society\\
Minor: Studio Art\\
Honors: Deans List, President’s Public Service Award
\vspace{4mm}

\end{document}